\chapter{Literature Review}
\label{chap:lr}

\chaptermark{Second Chapter Heading}

This chapter presents a comprehensive overview of existing research on remotely operated vehicles (ROVs),
focusing on modeling and control design. This literature review aims to investigate and synthesize
control strategies, addressing uncertainties from actuator dynamics and environmental factors, which
correspond to the proposed research question.

Section 1 gives a brief description of ROVs, including their types and general attributes.
Section 2 explains the commonly accepted assumptions and mathematical models used in the field.
Section 3 offers an extensive review of various studies on the application of robust control
design for underwater systems. In conclusion, Section 4 summarizes the key insights from the review
and suggests a control methodology.

\section{Overview on ROVs}
\todo{\#TODO Add more sorces and get more info about ROVs.}

    This section provides an overview of ROVs, from their classification and applications to their
    inherent characteristics and challenges. The obtained knowledge forms a basis for ROV modeling
    and control design.

    \temp{ROV physics -> complex model design}
    According to \cite{rov_review}, an ROV's mechanical structure consists of a monitoring camera, a sensor
    for gathering navigation data, and actuators for directional control. A
    comparative study \cite{overview} found that the physical aspects that affect ROV functions are the accuracy of
    sensor systems and the thruster designs. The unpredictable nature of underwater currents, drag,
    and buoyancy dynamics can also have a serious impact on a ROV's performance, complicating model
    design.

    \temp{Small ROVs are more preferrable -> wide range applications}
    A recent systematic review \cite{inspection_review} concluded that there are two primary classifications for ROVs based
    on their functions and intended use: observation class and work class. Observation class vehicles
    are typically small and limited to shallow waters with propulsion power up to a few kilowatts. Work
    class vehicles can perform heavy-duty work, requiring significant hardware
    system complexity. Thus, when the functionality of these large
    ROVs is not necessary, a smaller ROV is preferred for a wide range of applications.

    \temp{Applications of ROV -> control objectives}
    Several studies \cite{rov_review, overview} have identified that ROVs have become crucial for industrial applications,
    offshore oil and gas exploration, patrolling, and surveillance. Therefore, its control system
    should focus on position tracking and station keeping in the presence of parameter and environmental uncertainties, addressing the following issues.

    \todo{\#TODO Add connection to modelling, wrap it up}

\section{Mathematical Modelling}

    Remotely operated vehicles require mathematical models for various purposes, including control
    system design, simulation, and performance analysis.

    \temp{SRB}
    Thor I. Fossen \cite{fossen:guidance} provided a complete description of the fundamentals of mathematical modeling for marine
    vehicles. In his book, ROV was represented as a single rigid body (SRB) by considering 
    it as a solid mass with no internal movement or deformation. The SRB model has drastically simplified the modeling while capturing the essential
    dynamics of the system. 

    \temp{Kinematics and dynamics}
    From a kinematic
    point of view, ROVs have six degrees of freedom (DoFs). However, the orientation expressed
    in the rotation angles could eventually lead to the singularity. To solve this issue,
    \cite{quat_smc} proposed the quaternions representation. The dynamics was derived based on classical
    physics laws: Newton’s Second Law and Euler-Lagrange equation, forming the set of nonlinear equations.
    The study \cite{identification} simplified the equations and represented them in a matrix form.

    \temp{Parameter estimation}
    However, several sources have established that some aspects of the ROV dynamics require empirical
    estimates due to their complex, nonlinear, and coupled nature \cite{fossen:guidance, bluerov}. For instance, the inertia
    of the surrounding fluid cannot be neglected when the vessel moves through a viscous medium. Additionally, water damping is another source of nonlinearity that
    can be approximated as a function of the velocity. Finally, aside from buoyancy and
    gravity, it is common practice to cancel all other forces acting on a vehicle, although it can also impact the dynamics \cite{bluerov}.

    \temp{Thruster modelling}
    Moreover, thruster modeling must be applied to define the desired thrust of each thruster. A recent
    study by \cite{bluerov} stated that creating an accurate thruster model can be challenging due to the
    influence of factors such as motor models, hydrodynamic effects, and propeller mapping.
    
    \temp{Uncertaint model-> control objectives}
    By making these simplifications, the control system cannot independently provide effective control
    over such uncertain dynamics. As a result, a robust controller design is necessary for precise ROV
    position tracking.

\section{Control Solutions}

    \temp{Connect modelling and control}
    Controlling an ROV is a complex task that requires a set of processes to stabilize the vehicle and
    to make it follow the operator's instructions. To ensure the robustness of the system, it is
    necessary to define a control system that can handle disturbances caused by parameter and
    environmental changes. \\
    According to \cite{overview}, there are two main challenges associated with ROVs control:
    \begin{enumerate}
        \item Unmodeled elements like added mass and hydrodynamic coefficients.
        \item Highly nonlinear dynamics of the underwater environment which cause significant disturbances to the vehicle.
    \end{enumerate}

    \temp{Base approach -> SMC}
    The research on ROV control showed several schemes that can achieve robust stability under
    variable disturbances. The classical approach applied is sliding mode control (SMC), which was
    introduced by Slotine \cite{slotine}. SMC is an effective way to address the issues mentioned above and is,
    therefore, a feasible option for controlling underwater vehicles. However,
    standard SMC introduces high-frequency signals, which can cause actuator switching and consequently
    decrease its lifetime.

    \temp{Better SMC variations}
    \todo{\#TODO Change sources and control approaches}\\
    The modern SMC interpretations keep the main advantages,
    thus removing the chattering effects. One of the possible approaches is Adaptive Sliding Mode Control
    (ASMC) design. \cite{fossen:control} designed an effective hybrid control mechanism for the underwater system that
    follows a given route, adapting to dynamic disturbances. \cite{adaptive_smc} improved a control system for ROVs,
    eliminating the need for dynamics linearization. Another way to refine SMC is to add an integral
    component into the controller equation. The proposed Integral Sliding Mode Control (ISMC) reduced
    chattering, effectively eliminating the uncertainty of the model parameters \cite{integral_smc}.

    \temp{My proposal-> use optimization}
    \todo{\#TODO Connect previous part to my proposed control scheme}\\
    The choice of control strategy should be based on the specific
    requirements and characteristics of the underwater vehicle. While both SMC modifications showed
    precise control, these approaches faced certain challenges \cite{integral_smc}, \cite{adaptive_smc}. The ISMC method had limitations in adapting to rapidly changing dynamics, while the ASMC method experienced potential trade-offs in transient performance.
    These problems were opposite to each other. Therefore, combining them into Adaptive Integral Sliding
    Mode Control (ADISMC) can be a good idea to leverage the strengths of both methods and compensate
    for their weaknesses.

\section{Summary}
    \todo{\#TODO Change according to my proposed control scheme}

    This literature review comprehensively examined the general characteristics, mathematical modeling,
    and control solutions for underwater vehicles. This overview identified a gap in the field of robust
    control for remotely operated vehicles, particularly in dealing with parameter and environmental
    uncertainties. While the original sliding mode control scheme provided robust stability, it suffered
    from high-frequency output oscillations. There were several variations of SMC available, and each
    algorithm has its limitations. To address this research gap, a combination of adaptive and integral
    sliding mode modifications was proposed.